RESEARCH IN CONTEXT: Seed ecology of European mesic meadows

### 2021-10-20 doc/manuscript.Rmd
AoB 2nd revision 🍷

The mesic meadows of Europe are semi-natural open habitats that occupy clearings created by human intervention over a temperate wooded landscape [@RN5033; @RN5045], in sites with moderately fertile and well-drained soils [@RN4698]. Once, these were novel plant communities, with a composite flora made up of species from different ecological backgrounds. During historical times, their species composition further evolved following changes in human society and management practices [@RN5035; @RN5045]. Mesic meadows are thus the result of a process of habitat domestication that is characteristic of Europe's natural history [@RN5034]. Nowadays, mesic meadows maintained by agricultural practices are an essential aspect of European landscapes, both real [@RN4996] and fictional [@RN5029].

>>>>

The mesic meadows of Europe are semi-natural open habitats that occupy clearings created by human intervention over a temperate wooded landscape [@RN5033; @RN5045], in sites with moderately fertile and well-drained soils [@RN4698]. These novel anthropogenic plant communities, with a composite flora made up of species from different ecological backgrounds, have constantly changed in response to shifts in human society and associated management practices [@RN5035; @RN5045], but nonetheless characterise Europe's natural history [@RN4996].
